---
title: "Churn Analysis"
author: "Joe Barrett (jsb8vs)"
date: "Due Date: 11:59pm, Apr 12 (Tue)"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: hide
  pdf_document:
    toc: yes
#runtime: shiny
runtime: shiny
---

<style>
h1.title {
  font-size: 30px;
}
h1 {
  font-size: 26px;
}
h2 {
  font-size: 22px;
}
h3 { 
  font-size: 18px;
}

</style>

```{r, warning = FALSE}
library(knitr)

```

# Data

* Data used is accessed via the Oracle for Startups repo.  

* Many variables are available for access, I will be focussing on those bolded:
  1. ORDER_ID
  2. STARTUP_ID
  3. COUNTRY
  4. MIGRATION_STAGE
  5. SPM
  6. TOTAL_CONSUMPTION
  7. PAID_CONSUMPTION
  8. CREDIT_CONSUMPTION
  9. REGION
  10. PROFILE_CREATED (REMOVE)
  11. CLOUD_USAGE

  17. INDUSTRY1
  18. INDUSTRY2
  19. INDUSTRY3
  20. TECHNOLOGY1
  21. TECHNOLOGY2
  22. TECHNOLOGY3
  23. DESCRIPTION_PROVIDED (REMOVE)


```{r, message=FALSE, include=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
library(ggplot2)
library(devtools)
library(knitr)
library(ggjoy)
library(kableExtra)
library(tidyverse)
library(lubridate)

```


# Data

## Accessting Data

```{r}
# Cloud Orders
library(readr)
cloud_orders <- read.csv("Data/cloud_orders.csv")
cloud_orders <- subset(cloud_orders, select = -c(EXTENSION,
                                                 ENROLLMENT_DATE,
                                                 NS_INTERNAL_ID,
                                                 PAYING_CUSTOMER_DATE,
                                                 PAYING_CUSTOMER_DATE,
                                                 PRODUCTION_STAGE,
                                                 MENTORSHIP_MILESTONES,
                                                 PAYING_CUSTOMER,
                                                 MENTORSHIP_MILESTONES
                                                 ))
#head(cloud_orders)

# Daily_consumption
daily_consumption <- read.csv("DATA/daily_consumption.csv")
daily_consumption <- subset(daily_consumption, select = -c(CONSUMPTION_DATE))

head(daily_consumption)
# mc_data_v
mc_data_v <- read.csv("Data/mc_data_v.csv")
mc_data_v <- subset(mc_data_v, select = -c(USAGE_COMPLETION_DATE,
                                           CASE_STUDY,
                                           CASE_STUDY_LAST_UPDATE_DATE,
                                           REF_ARCH_COMMENTS,
                                           REF_ARCH_LAST_UPDATE_DATE,
                                           IS_DATE,
                                           ELEVATOR_PITCH_LAST_UPDATE_DATE,
                                           VECTOR_LOGO_LAST_UPDATE_DATE,
                                           MAIL_SENT_DATE,
                                           LAST_UPDATE_DATE,
                                           PROFILE_CREATION_DATE,
                                           ELEVATOR_PITCH,
                                           MAIL_SENT,
                                           LOGO_FILE_COUNT,
                                           NS_INTERNAL_ID,
                                           REF_ARCH_FILE_COUNT,
                                           REF_ARCH_WORKLOAD,
                                           REF_ARCH,
                                           IS_SOLUTION_FLAG,
                                           IS_SOLUTION,
                                           IS_INTEGRATION_FLAG,
                                           VECTOR_LOGO
                                           ))
#head(mc_data_v)

# monthly_usage
monthly_usage <- read.csv("Data/monthly_usage.csv")
monthly_usage <- subset(monthly_usage, select = -c(ORDER_ID
                                                   ))

#head(monthly_usage)


startup_details <- read.csv("Data/startup_details.csv")
startup_details <- subset(startup_details, select = -c(REGION_CODE,
                                                       COUNTRY,
                                                       DIGITAL_CATALOUGE,
                                                       MENTOR_BENEFIT,
                                                       MIGRATION_BENEFIT,
                                                       FUNDRAISING_ACTIVE_FLAG,
                                                       STAGE))



```

## Filtering Data

```{r}
df <- cloud_orders %>% right_join(daily_consumption)

df2 <- df %>% right_join(mc_data_v)

df3 <- df2 %>% right_join(startup_details)

all_data <- df3

head(all_data)
colnames(all_data)

all_data <- subset(all_data, select = -c(PROFILE_CREATED,
                                         INTEGRATION_STRATEGY,
                                         MC_COMPLETE_STATUS,
                                         CLOUD,
                                         PK_USAGE,
                                         PROMOTION_KIT_FLAG))
```

## A quick view

```{r, warning=FALSE, message=FALSE}
# Printing out the first few rows of data
all_data_clean <- na.omit(all_data)
kable(head(all_data_clean), booktabs = TRUE) %>% kable_styling(font_size = 13)

```

## Data Validation

TOTAL_CONSUMPTION	
```{r}
map(all_data_clean, class)
```
All features appear to have the associated data type. Null values were removed. 

# Plots

## Country X Tech X Cloud Usage

```{r, out.height="100%", message=FALSE}

shinyApp(
  ui <- fluidPage(
  sliderInput("span4", label = "Span adjustment:",
              min = 0.2, max = 0.9, value = 0.5, step = 0.1),
  plotOutput("all_data_clean")
  ),
  
  server <- function(input, output){
    output$all_data_clean <- renderPlot({
    ggplot(all_data_clean, aes(x = COUNTRY, y = CLOUD_USAGE)) + 
        geom_point(aes(color = MIGRATION_STAGE)) + 
        geom_hline(data = median(all_data_clean$CLOUD_USAGE)) +
        
        geom_smooth(data = all_data_clean, aes(x = COUNTRY, Y = CLOUD_USAGE),
                    method="loess", 
                    formula=y~x, 
                    se=FALSE, 
                    span=input$span4,
                    color = "red")+
        theme_bw() +
        labs (title = "",
              x = "",
              y = "")+
        theme(axis.text.x = element_text(angle=90, hjust=1))
      })}
)   
```

```{r pressure, echo=FALSE, include=FALSE}
library(ggplot2)

all_data <- na.omit(all_data)
med <- median(all_data$CLOUD_USAGE)
med
ggplot(data = all_data, aes(x=INDUSTRY2, y=CLOUD_USAGE)) +
  geom_bar(stat = "identity", aes(fill = COUNTRY)) + 
  labs (x = "Tech Sector",
        y = "Cloud Usage",
        title = "Cloud Usage by Tech Sector")+
  geom_hline(yintercept = med, aes(color = Red))+
  theme(plot.title=element_text(hjust=0.5), axis.text.x = element_text(angle = 45, hjust = 1))
```

## Plotly

```{r, include=FALSE}
library(plotly)

plotly_data <- subset(all_data, select = c(INDUSTRY2, CLOUD_USAGE, COUNTRY))

plotly_data <- na.omit(plotly_data)

ggplotly(ggplot() + 
           geom_point(data = plotly_data, aes(x = INDUSTRY2, y = CLOUD_USAGE, color = COUNTRY)) + 
           labs(x = 'Tech Sector', 
                y = 'Cloud Usage', 
                title = 'Usage by Tech Sector')+
           geom_smooth(data = plotly_data, aes(x = INDUSTRY2, y = CLOUD_USAGE, color = COUNTRY), se = FALSE, method = "loess") +
           theme(plot.title=element_text(hjust=0.5), axis.text.x = element_text(angle = 45)))

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
